Implicit yaddayadda

### 2011-10-27 papers/PLDI2012/implicitization.tex
+description implem

This motivates a key implement decision of our tool: only those variables $v_1,\dots,v_n$ that are not defined by arithmetic operations are retained as coordinates in the abstract domain (e.g. as dimensions in polyhedra). A basic block of code therefore amounts to a \emph{parallel assignment} operation
$(v_1,\dots,v_n) \allowbreak\mapsto\allowbreak
(f_1(v_1,\dots,v_n), \allowbreak, \dots, \allowbreak
 f_n(v_1,\dots,v_n))$;
such operations are directly supported by APRON.
A first benefit is to limit the number of dimensions in the abstract values, since polyhedra libraries typically perform worse with higher dimensions. TODO
Note that this means that the abstract operation for a single path in path-focusing methods also is a (large) parallel assignment.

@@

>>>>

This motivates a key implement decision of our tool: only those variables $v_1,\dots,v_n$ that are not defined by arithmetic operations are retained as coordinates in the abstract domain (e.g. as dimensions in polyhedra). A basic block of code therefore amounts to a \emph{parallel assignment} operation
$(v_1,\dots,v_n) \allowbreak\mapsto\allowbreak
(f_1(v_1,\dots,v_n), \allowbreak, \dots, \allowbreak
 f_n(v_1,\dots,v_n))$;
such operations are directly supported by APRON.
A first benefit is to limit the number of dimensions in the abstract values, since polyhedra libraries typically perform worse with higher dimensions.
A second benefit is that the abstract operation for a single path in path-focusing methods also is a (large) parallel assignment.

We further reduce the number of variables by projecting out those that are not live at the program point. Again, SSA use-def and def-use chains make it easy to compute liveness.

@@

Our implementation of path-focusing currently does not use true acceleration techniques, as proposed by \citet{Monniaux_Gonnord_SAS11}. Instead, it simply runs widening and narrowing iterations on a single path.
